\chapter{Related Work}

Object tracking is an old problem that has been tackled a lot of times with a lot of different viewpoints. For example, one of the more common approaches is to use multiple camera setups. Quanzeng et. al. \cite{1} are using a multi-camera setup to track people in 3D in real-time using deep learning. Andreas et. al. \cite{2} specifically implement a multi-camera solution for tracking vehicles. Ruiheng et. al. \cite{3}  implement a multi-camera strategy along with deep learning to identify and track multiple players in athletics. Yuhang et. al. \cite{4} try to implement a multi-camera strategy to track multiple targets at once, like people moving around in a room. Multi-camera, multi-target tracking strategies are quite famous and widely studied. Peng Li et. al. \cite{5} have also tried to implement a multi-camera, multi-target tracking strategy with re-identification features.\newline

Other approaches have also been studied. For example, Cheng et. al. \cite{6} propose a single framework to segment and track objects but in different modes. Stephan et. al. \cite{7} propose a distributed strategy to divide the recognition and tracking into server and client-side tasks. Yuri Mikawa et. al. \cite{8} have proposed an interesting approach to tracking objects along with their orientations in big areas. They use an array of LED markers placed on the subject in consideration and then depending on the orientation and combination of LEDs visible to the camera, they estimate the position and the orientation of the object. Youngmin Park et. al. \cite{9} have proposed an approach to track multiple 3D objects together; however, they require the CAD models of the objects they want to track. Adel et. al. \cite{10} proposed a pipeline to track object poses in 3D; however, they track the 3D  bounding boxes around the objects in the image space.\newline

Most of the currently existing research on 3D tracking either uses multiple cameras or sensor arrays to be able to track the objects/people in 3D space whereas the research that does not use multiple cameras or sensor arrays does not truly track the objects/people in 3-dimensional space. There is a gap in the research, and through the scope of this thesis, we will try to bridge this gap. 
